---
title: "readme"
author: "Varsha Ujjinni Vijay Kumar"
date: "07/06/2021"
output: 
    html_document:
        theme: sandstone
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Hey everyone!! Thank you for taking your time in looking at this repository for the **Road Accidents in Australia** dashboard. As the data for this dashboard is really big, it is very clumsy to upload all of the data sets for the proper working of the shiny dashboard. 

Please follow the following steps to get the data in the form that is needed to get the appropriate data for its working. 

1. The data is taken from [here](https://www.kaggle.com/mgray39/australia-new-zealand-road-crash-dataset), please download all of the tables present in this data set.

2. After downloading all of the tables from the above link, create a RMD file and use the follwing code for its reading:

```{r readdata,eval=FALSE}
casualty <- read.csv(here::here("data","Casualties.csv"))
crash <- read.csv(here::here("data","Crash.csv"))
date <- read.csv(here::here("data","DateTime.csv"))
descp <- read.csv(here::here("data","Description.csv"))
loc <- read.csv(here::here("data","Location.csv"))
veh <- read.csv(here::here("data","Vehicles.csv"))
crash <- read.csv(here::here("data","Crash.csv"))
```

3. Use the following tidy code for the datasets:

```{r datatidy,eval=FALSE}
casualty <- read.csv(here::here("data","Casualties.csv")) %>%
  select(-X) %>%
  na.omit()

date <- read.csv(here::here("data","DateTime.csv")) %>%
  select(-c(X, day_of_month))

descp <- read.csv(here::here("data","Description.csv"))%>%
  select(-X)

loc <- read.csv(here::here("data","Location.csv")) %>% filter(country == "AU") %>%
  na.omit() %>%
  select(-X)

veh <- read.csv(here::here("data","Vehicles.csv"))
accidents <- crash %>%
  left_join(casualty, by = "casualties_id") %>%
  left_join(date, by = "date_time_id") %>%
  left_join(descp,by = "description_id") %>%
  left_join(loc, by = "lat_long") %>%
  left_join(veh, by = "vehicles_id") %>%
  select(-c(X.x,X.y))

write.csv(here::here("data","accidents.csv"))
```


4. Finally use this data and run the app.R file for the shiny dashboard. 


